Scalar and Representative Observables, and Their Associated Statistical Model, for Polarimetric SAR Data

### 2014-08-12 paper_dev/article.tex
auto

Since the elementary components follow fixed distributions (i.e. $\chi^2(2L)$),
  it is natural that this variable also follows a fixed distribution.
Moreover, it is independent of the underlying signal $\Sigma_v$,
  indicating its statistically consistent properties and hence its applicability as a POLSAR discrimination measure.
This claim is extrapolated from the widely-used intensity-ratio as a SAR discrimination measure
  and will be further discussed in the next sections.
%is further strengthened in the next section which shows that the generic models for POLSAR presented in this paper also include the commonly-used models for SAR as its special 1-dimensional case. 
%This result shows how
%In short, these random variables are shown to follow consistent and fixed distributions,
%  regardless of the underlying signal $\Sigma_v$.

>>>>

Since the elementary components follow fixed distributions (i.e. $\chi^2(2L)$),
  it is natural that this variable also follows a fixed distribution.
Moreover, it is independent of the underlying signal $\Sigma_v$,
  indicating its statistically consistent properties and hence its applicability as a POLSAR discrimination measure.
$\mathbb{R}_C$ can be used, for example, in change detection application similar to that proposed in \cite{Conradsen_2003_TGRS_4}.
At the same time, $\mathbb{R}_{\Sigma}$ can be used in classification or segmentation applications, similar to those proposed in \cite{Kersten_2005_TGRS_519, Lee_2011_IGARSS_3740, Cao_2007_TGRS_3454}.
This claim is extrapolated from the widely-used intensity-ratio as a SAR discrimination measure \cite{Rignot_1993_TGRS_896}.
This will be further discussed in the next sections.
%is further strengthened in the next section which shows that the generic models for POLSAR presented in this paper also include the commonly-used models for SAR as its special 1-dimensional case. 
%This result shows how
%In short, these random variables are shown to follow consistent and fixed distributions,
%  regardless of the underlying signal $\Sigma_v$.
